\section{Method}
\label{sec:method}

\Cref{fig:architecture} gives the full picture.
Frames arrive one at a time from a live video stream. At each step $t$, the Semantic Keyframe Memory (\cref{sec:skm}) scores the new frame $I_t$ and decides whether to store it in a bank of at most $N$ entries.
Independently, a user may submit a question $q$ at any moment.
The Temporal Query Router (\cref{sec:tqr}) classifies $q$ into a temporal scope and passes only the matching memory entries forward.
The Stream-Fused Generator (\cref{sec:sfg}) then runs a two-stage perception-synthesis pipeline over those entries and returns an answer in under 200\,ms.

\subsection{Semantic Keyframe Memory}
\label{sec:skm}

A live video stream produces frames at 15 to 30 fps. Consecutive frames are redundant.
Storing all frames is not feasible. Uniform subsampling loses rare but informative events.
The SKM retains frames based on visual-semantic importance.

\paragraph{Visual encoding.}
Each incoming frame $I_t$ passes through a CLIP ViT-B/32~\cite{radford2021clip} encoder, producing a 512-dimensional embedding $v_t$.
Not every frame goes through encoding. By default the system processes every 5th frame, giving 3 to 6 candidates per second and keeping encoding cost low.
The system saves a small JPEG thumbnail alongside each embedding for later visualization.

\paragraph{Importance scoring.}
The system scores every candidate against what is already in memory. Two signals determine the score.

\textbf{Visual novelty} captures how different the candidate looks. We compute the cosine similarity between $v_t$ and each stored embedding, and one minus the maximum gives the novelty. If every stored frame looks similar to the candidate, novelty is low. If no stored frame is close, novelty is high.

\textbf{Temporal coverage} captures how well the candidate fills a gap in the timeline. It is the smallest absolute time difference between $t$ and any stored timestamp, divided by a horizon $T_{\max}$.

The importance score for frame $I_t$ is:
\begin{equation}
\begin{split}
  s(I_t) =\; & \alpha \Bigl(1 - \max_{j \in \mathcal{M}} \cos(v_t, v_j)\Bigr) \\
  & + (1{-}\alpha)\,\min\!\Bigl(\frac{\min_{j \in \mathcal{M}} |t - t_j|}{T_{\max}},\, 1\Bigr)
\end{split}
  \label{eq:importance}
\end{equation}
where $\mathcal{M}$ is the current memory set, $\alpha = 0.7$ controls the novelty-coverage trade-off, and $T_{\max} = 300$\,s (5 minutes). A frame that is both visually distinct and temporally distant from stored entries receives the highest score.

\paragraph{Memory update.}
Below capacity, every candidate enters memory directly.
Once memory is full, the system re-scores stored entries and finds the lowest-scoring one. If the incoming candidate scores higher, it replaces that entry. If not, the system drops the candidate. The full update runs in $O(N)$ time and adds under 4\,ms of latency.

\paragraph{Temporal bookkeeping.}
Each memory entry stores its original timestamp. The TQR uses these timestamps to filter entries by time window. We sort memory by timestamp after each insertion.


\subsection{Temporal Query Router}
\label{sec:tqr}

When a question $q$ arrives, the TQR determines which part of memory is relevant.
The pipeline has three stages: a keyword matcher scores the query against per-scope keyword lists, a scope selector picks the best temporal scope, and a memory filter returns only entries in the matching time window.

\paragraph{Scope classification.}
The TQR assigns each question one of three temporal scopes: \textsc{instant}, \textsc{recent}, or \textsc{historical}.
A keyword matcher runs over the lowercased query string.
Three manually curated keyword lists drive the decision. \textsc{Instant} cues include ``right now,'' ``currently,'' and ``at this moment.'' \textsc{Recent} cues include ``just,'' ``a moment ago,'' ``few seconds,'' and ``last minute.'' \textsc{Historical} cues include ``earlier,'' ``before,'' ``previously,'' and ``how many times.''

The scope with the most keyword hits wins. When no keyword matches or two scopes tie with low confidence (top score / total $<$ 0.6), the system defaults to \textsc{historical}, granting full memory access. This fallback is conservative: an over-broad context is better than a truncated one.

\paragraph{Adapting to event density.}
The three scopes are defined linguistically, not temporally: they reflect how the user phrases the question rather than imposing fixed time ranges.
In practice, different video streams exhibit different event densities.
A surveillance feed may show one event per minute, while an egocentric cooking stream can produce rapid transitions every few seconds.
The recency window $W$ mediates this mismatch.
When $W = 30$\,s, the \textsc{recent} scope captures roughly the last 3--5 events in a high-density cooking stream or the last 0--1 events in a slow surveillance feed.
If the density is so low that no events fall within $W$, the conservative default to \textsc{historical} ensures the system searches the full memory rather than returning an empty context.
We chose a single $W$ for simplicity; an adaptive scheme that estimates event density from the SKM insertion rate could refine this boundary, but in our experiments the fixed value works well across all evaluated domains (\cref{sec:experiments}).

\paragraph{Scope-aware filtering.}
Given predicted scope $c$ and current time $t_{\text{now}}$, the filtered subset $\mathcal{F} \subseteq \mathcal{M}$ is:
\begin{equation}
  \mathcal{F} \!=\!
  \begin{cases}
    \{\argmax_{j \in \mathcal{M}} t_j\}                        & c = \text{inst.} \\[3pt]
    \{j \!\in\! \mathcal{M} : t_j \!\ge\! t_{\text{now}} - W\} & c = \text{rec.}  \\[3pt]
    \mathcal{M}                                                 & c = \text{hist.}
  \end{cases}
  \label{eq:scope_filter}
\end{equation}
where $W = 30$\,s is the recency window. \textsc{inst.}, \textsc{rec.}, and \textsc{hist.}\ stand for the three scopes defined above. Only entries in $\mathcal{F}$ reach the Stream-Fused Generator.


\subsection{Stream-Fused Generator}
\label{sec:sfg}

The SFG turns filtered keyframes into a natural-language answer through two stages. \Cref{alg:sfg} gives the full procedure.

\paragraph{Stage 1: BLIP visual perception.}
The system samples up to $K\!=\!6$ frames from the filtered set $\mathcal{F}$ (or takes all of them if $|\mathcal{F}| \le K$).
When $|\mathcal{F}| > K$, we select uniformly spaced indices to preserve temporal coverage.
For non-instant queries, the most recent frame is always appended to the sampled set, anchoring the answer in the present even when the question targets the past.
Two BLIP~\cite{li2022blip} models process each sampled frame $I_k$ independently:

\begin{itemize}[itemsep=2pt]
  \item \textbf{BLIP captioning} (blip-image-captioning-base): generates a free-form description of the frame contents. Each caption is at most 50 tokens.
  \item \textbf{BLIP VQA} (blip-vqa-base): takes the user's question $q$ and the frame $I_k$ as input. It produces a short direct answer for that specific frame. Each answer is at most 30 tokens.
\end{itemize}

The system collects all captions and VQA answers into a pool of textual observations, then deduplicates and ranks them by frequency. Observations that appear across multiple frames carry more weight in the final answer.

\paragraph{Stage 2: Flan-T5 language synthesis.}
The system assembles a structured prompt containing the user's question, deduplicated captions, deduplicated VQA outputs, and the sampled-frame count. The format differs for yes/no versus open-ended questions.
Flan-T5-base~\cite{chung2022flanT5} generates up to 80 tokens with beam search (4 beams, length penalty 1.0, no-repeat 3-gram constraint), producing one coherent answer from multiple keyframes.
When Flan-T5 is unavailable, the system falls back to template concatenation.

\begin{algorithm}[t]
\SetAlgoLined
\KwIn{Question $q$, memory $\mathcal{M}$, time $t_{\text{now}}$}
\KwOut{Answer string $a$}
$c \leftarrow \texttt{TQR}(q)$ \tcp*{scope classification}
$\mathcal{F} \leftarrow \texttt{ScopeFilter}(\mathcal{M}, c, t_{\text{now}})$\;
$S \leftarrow \texttt{Sample}(\mathcal{F}, K\!=\!6)$\;
\If{$c \neq \text{instant}$}{
  $S \leftarrow S \cup \{\argmax_{j \in \mathcal{M}} t_j\}$ \tcp*{append live frame}
}
$\mathcal{C}, \mathcal{V} \leftarrow \emptyset, \emptyset$\;
\ForEach{frame $I_k \in S$}{
  $\mathcal{C} \leftarrow \mathcal{C} \cup \{\texttt{BLIP-Cap}(I_k)\}$\;
  $\mathcal{V} \leftarrow \mathcal{V} \cup \{\texttt{BLIP-VQA}(I_k, q)\}$\;
}
$p \leftarrow \texttt{BuildPrompt}(q, \texttt{dedup}(\mathcal{C}), \texttt{dedup}(\mathcal{V}))$\;
$a \leftarrow \texttt{Flan-T5}(p)$\;
\Return{$a$}
\caption{Stream-Fused Generator}
\label{alg:sfg}
\end{algorithm}

\paragraph{Latency budget.}
The total per-query latency breaks down as follows. TQR scope classification takes about 1\,ms. Frame sampling and BLIP inference on 6 frames takes 80 to 120\,ms. Flan-T5 decoding takes 60 to 80\,ms.
End-to-end latency stays under 200\,ms on a single NVIDIA A100. The two BLIP models (captioning and VQA) share the same vision backbone, so the feature extraction cost is amortized across both tasks.


\subsection{Training and Hyperparameters}
\label{sec:training}

Every model in the pipeline is a frozen pre-trained checkpoint; no end-to-end training is required.
The vision encoder is CLIP ViT-B/32~\cite{radford2021clip} (224$\times$224 input, 512-d embeddings).
Two BLIP~\cite{li2022blip} checkpoints handle perception: blip-image-captioning-base and blip-vqa-base, both loaded in evaluation mode.
The language synthesis model is Flan-T5-base~\cite{chung2022flanT5}, instruction-tuned on 1,836 tasks.
We selected $\alpha$ and $T_{\max}$ by sweeping $\alpha \in \{0.5, 0.6, 0.7, 0.8\}$ and $T_{\max} \in \{60, 120, 300, 600\}$ on a held-out set, choosing the best combination ($\alpha = 0.7$, $T_{\max} = 300$\,s) by LiveQA-Bench accuracy.
TQR keyword lists were compiled by hand from annotated question-scope pairs in the LiveQA-Bench training split and validated on a held-out split.
